# CUSTOMER PERSONALITY ANALYSIS

```{r}
getwd()
```

```{r}
setwd("C:/Users/parul/Desktop/Congno Rise Internship")
```

1.  Loading the Dataset

```{r}
customer_analysis<-read.csv("C:/Users/parul/Desktop/Congno Rise Internship/customer_analysis.csv")
```

```{r}
customer_analysis
```

2.  Downloading the packages required

```{r}
install.packages("ggplot2")
library("ggplot2")
```

```{r}
install.packages("dplyr")
library("dplyr")
```

```{r}
install.packages("tidyr")
library("tidyr")
```

```{r}
install.packages("lubridate")
library("lubridate")
```

```{r}
install.packages("car")
library("car")
```
```{r}
library("corrplot")
```

3.  We'll clean the data
4.  Convert Dt_Customer to Data type for time based analysis

```{r}
customer_analysis$Dt_Customer<-as.Date(customer_analysis$Dt_Customer)
```

```{r}
customer_analysis
```

5.  Calculate Age from Year_Birth for demographic Analysis

```{r}
customer_analysis$Age<- as.numeric(format(Sys.Date(),"%Y"))-customer_analysis$Year_Birth
```

```{r}
customer_analysis
```

6.  Impute missing values in the Income column with the median

```{r}
customer_analysis$Income[is.na(customer_analysis$Income)]<-median(customer_analysis$Income,na.rm = TRUE)
```

```{r}
customer_analysis
```

7.  DATA VISUALISATION
8.  Age Distribution of Customers

```{r}
ggplot(customer_analysis,aes(x=Age))+
  geom_histogram(bins=30,fill="peachpuff",color="thistle")+
  theme_minimal()+
  labs(title = "Age Distribution of Customers",x="Age",y="Frequency")
```

THIS HISTOGRAM SHOWS THAT A RANGE OF CUSTOMERS LIE IN THE AGE GROUP OF 45-55 YEARS.

9.  Income Distribution of Customers

```{r}
ggplot(customer_analysis,aes(x=Income))+
  geom_histogram(bins=30,fill="#062C60",color="black")+
  theme_minimal()+
  labs(title = "Income Distribution of Customers",x="Income",y="Frequency")+

```

THE GRAPH SHOWS THAT THE MOSTLY CUSTOMERS HAVE A MODERATE INCOME.

10. Education level of Customers

```{r}
ggplot(customer_analysis)+
  geom_bar(aes(x=reorder(Education,Education,function(x)-length(x))),
           fill="#2D5792")+
  theme_minimal()+
  labs(title = "Education Level of Customers",x="Education Level",y="Count")+
  coord_flip()
```

MOST CUSTOMERS ARE WELL EDUCATED AND HAVE COMPLETED THEIR GRADUATION.

11. Marital Status of Customers

```{r}
ggplot(customer_analysis)+
  geom_bar(aes(x=reorder(Marital_Status,Marital_Status,function(x)-length(x))),
           fill="#9F87E3")+
  theme_minimal()+
  labs(title = "Marital Status of Customers",x="Marital Status",y="Count")+
  coord_flip()
```

THIS SHOWS THAT MOSTLY CUSTOMERS ARE MARRIED

12. Total spending in Different Categories

```{r}
customer_analysis$Total_Spending<-rowSums(customer_analysis[,c("MntWines","MntFruits","MntMeatProducts","MntFishProducts","MntSweetProducts","MntGoldProds")])
```

```{r}
customer_analysis
```

```{r}
hist(customer_analysis$Total_Spending,main = "Total Spending of Customers",xlab = "Total Spending",col="#35063E")
```

13. Total Spending VS Age

```{r}
ggplot(customer_analysis,aes(x=Age,y=Total_Spending))+
  geom_point(aes(color=Marital_Status),alpha=0.6)+
  theme_minimal()+
  labs(title = "Total Spending VS Age",x="Age",y="Total Spending")
```

MARRIED AND SINGLE PEOPLE IN THE AGE GROUP OF 30-75 YEARS SPEND THE MOST

14. Total Spending VS Income

```{r}
ggplot(customer_analysis,aes(x=Income,y=Total_Spending))+
  geom_point(aes(color=Education),alpha=0.6)+
  theme_minimal()+
  labs(title = "Total Spending VS Income",x="Income",y="Total Spending")
```
14. Running a Regression
```{r}
regn<-lm(Total_Spending~Income,data=customer_analysis)
```

```{r}
regn
```

```{r}
summary(regn)
```

```{r}
#As Income increases by 1 unit the total spending increases by approx 0.016 units
#p-value is very small which means that income has a significant effect on total #spending
```
15. Total Spending by Education
```{r}
ggplot(customer_analysis,aes(x=Total_Spending,y=Education))+
  geom_boxplot(fill="lightblue")+
  theme_minimal()+
  labs(title = "Total Spending by Education Level",x="Total Spending",y="Education")
```
HIGHER EDUCATION LEVELS, CORRESPONDS TO HIGHER LEVEL OF SPENDINGS

16. Total Spending by Marital Status
```{r}
ggplot(customer_analysis,aes(x=Total_Spending,y=Marital_Status))+
  geom_boxplot(fill="#C25283")+
  theme_minimal()+
  labs(title = "Total Spending by Marital Status",x="Total Spending",y="Marital Status")
```
THERE LIES SOME OUTLIERS IN THE CASE OF CUSTOMERS WHO LIVE TOGETHER & WHO ARE MARRIED

17. Corrplot
```{r}
numeric_columns<-sapply(customer_analysis,is.numeric)
```

```{r}
numeric_columns
```
```{r}
corr_mat<-cor(customer_analysis[,numeric_columns],use="complete.obs")
```
```{r}
corrplot(corr_mat,method = "circle",tl.srt=45,type="upper",tl.cex = 0.5,tl.col = "black")
```

